%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Enterprise Data Catalog} % Job title
    {data.world} % Organization
    {Austin, Texas} % Location
    {Nov. 2017 - Present} % Date(s)
    {
      \begin{cvsubentries}
       \cvsubentry
         {Senior Product Engineer}
         {Aug. 2021 - Present}
         {
          \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Mentor new hires and lead code reviews.}
            \item {Own critical product modules, ensuring reliability and scalability.}
            \item {Led a major re-theming project to modernize the look and feel of the product, laying the groundwork for future support for multiple themes such as light and dark mode.}
            \item {Architected and implemented complex data editing workflows, enabling advanced user interactions and streamlined data management.}
          \end{cvitems}
         }
       \cvsubentry
         {Product Engineer}
         {Mar. 2019 - Aug. 2021}
         {
          \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Led the end-to-end development and launch of a new data lineage feature, enabling users to visualize complex data relationships.}
            \item {Implemented advanced search and filtering capabilities, significantly enhancing user experience and data discoverability.}
            \item {Integrated third-party authentication (OAuth, SSO) to streamline onboarding for enterprise customers.}
          \end{cvitems}
         }
       \cvsubentry
         {Associate Software Engineer}
         {Nov. 2017 - Mar. 2019}
         {
          \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Designed and implemented an Excel integration enabling seamless, bi-directional data synchronization between Excel and data.world.}
            \item {Developed an Extract, Transform, Load (ETL) application to automate data synchronisation across diverse sources and targets.}
            \item {Engineered the company's Tableau Web Data Connector, empowering users to visualize and analyze data.world datasets directly within Tableau.}
          \end{cvitems}
         }
      \end{cvsubentries}
    }

%---------------------------------------------------------
  \cventry
    {Design Agency} % Job title
    {Metalab} % Organization
    {Victoria, British Columbia} % Location
    {Feb 2017 - Nov 2017} % Date(s)
    {
      \begin{cvsubentries}
       \cvsubentry
         {Junior Software Engineer}
         {Feb 2017 - Nov 2017}
         {
          \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Implemented a redesign of the company’s marketing website, translating design specifications into a modern, engaging, and high-performing user experience.}
          \end{cvitems}
         }
      \end{cvsubentries}
    }

%---------------------------------------------------------
  \cventry
    {Job Placement Network} % Job title
    {Andela} % Organization
    {Nairobi, Kenya} % Location
    {Feb 2016 - Jan 2020} % Date(s)
    {
      \begin{cvsubentries}
       \cvsubentry
          {Fellow}
          {Feb 2016 - Jan 2020}
          {
            \begin{cvitems} % Description(s) of tasks/responsibilities
              \item {Completed an intensive training course on the JavaScript ecosystem and essential programming tools, building a strong foundation in modern web development.}
              \item {Received targeted training in soft skills crucial for success in professional environments, including communication, teamwork, adaptability, and stakeholder management.}
              \item {Actively participated in the recruitment and onboarding of new hires, providing mentorship and guidance to accelerate their integration and professional growth within the organization.}
            \end{cvitems}
          }
      \end{cvsubentries}
    }

%---------------------------------------------------------

\end{cventries}
